Model LF

### 2022-09-27 max_dp endogen stød.Rmd
commit

  stat_reg = TIMESERIES(c(stat_reg),   
                       START=c(2006,1),FREQ=4),
  stat_tilpas = TIMESERIES(c(stat_tilpas),   
                       START=c(2006,1),FREQ=4),
  tilpas_pr = TIMESERIES(c(tilpas_pr),   
                       START=c(2006,1),FREQ=4),
  kuld_shock = TIMESERIES(c(kuld),   
                       START=c(2005,2),FREQ=4),
  ## Price adjustments
  pg_adj = TIMESERIES(c(pg_adj),   
                       START=c(2005,2),FREQ=4),
  p_bd_adj = TIMESERIES(c(p_bd_adj),   
                       START=c(2005,2),FREQ=4),
  p_equip_adj = TIMESERIES(c(p_equip_adj),   
                     START=c(2005,2),FREQ=4),
  px_adj = TIMESERIES(c(px_adj),   
                        START=c(2005,2),FREQ=4),
  ## Households

@@

#S_modelData$shock_kuld_model = shock_kuld_model

>>>>

  stat_reg = TIMESERIES(c(stat_reg),   
                       START=c(2006,1),FREQ=4),
  stat_tilpas = TIMESERIES(c(stat_tilpas),   
                       START=c(2006,1),FREQ=4),
  tilpas_pr = TIMESERIES(c(tilpas_pr),   
                       START=c(2006,1),FREQ=4),
  shock_kuld = TIMESERIES(c(kuld),   
                       START=c(2005,2),FREQ=4),
  ## Price adjustments
  pg_adj = TIMESERIES(c(pg_adj),   
                       START=c(2005,2),FREQ=4),
  p_bd_adj = TIMESERIES(c(p_bd_adj),   
                       START=c(2005,2),FREQ=4),
  p_equip_adj = TIMESERIES(c(p_equip_adj),   
                     START=c(2005,2),FREQ=4),
  px_adj = TIMESERIES(c(px_adj),   
                        START=c(2005,2),FREQ=4),
  ## Households

@@

#S_modelData$shock_kuld = kuld
